---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# homebuyer package

<!-- badges: start -->
<!-- badges: end -->

The goal of homebuyer is to provide functions that help new-homebuyers manage their finances. It currently only contains one function `m_to_save_down_deposit`, which allows you to calculate the months needed to save for a downpayment of a house given your income and investments.

## Installation

You can install the development version of homebuyer from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2022/assignment-b1-and-b2-karanvirsingh99")
```

## Example

This is a basic example which shows you how to use the `m_to_save_down_deposit` function

```{r example}
library(homebuyer)

# How many months until I can save for a 1,000,000 house with a 150,000 income,
# saving 10% of my income every month, and investing it with a return rate of 0.04

m_to_save_down_deposit(150000, 1000000, 0.1, 0.04)
```


